---
title: "Systems Project Crop Productivity"
author: "Kolby Grint"
date: "11/10/2020"
output:
  pdf_document: default
  html_document: default
---


```{r, include= FALSE}
library(car)
library(ggplot2)
library(emmeans)
library(lme4)
library(lmerTest)
library(patchwork)
library(glmmTMB)
library(tidyverse)
```


```{r}
data = read_csv("SystemsProjectMasterDataforR.csv") %>% 
  mutate_if(is.character, as.factor) %>% 
  janitor::clean_names() %>% 
  mutate(
    year = as_factor(year),
    rep = as_factor(rep)
  )
data
```

```{r}
corn = filter(data, crop == "Corn")
soybean= filter(data, crop == "Soybean")
```


# Corn Yield

### Model and ANOVA

```{r}
cn.mod = lmer(yield ~ site_crop_yr * soil * pre + (1 | site_crop_yr : rep), data = corn)
```


```{r, echo= FALSE}
qqnorm(resid(cn.mod))

plot(cn.mod)
```
I think assumptions for normality and equal variance are met.


```{r}
anova(cn.mod)
#Soil and site-crop-year fixed effects and Site-year:Soil was significant
```

Site-crop-year:soil management interaction, soil management fixed effect, and site-crop-year fixed effect are all significant. Proceeded to separate means by looking at soil management practices within each site-crop-year. Results displayed in the figure below.

```{r}
emmip(cn.mod, ~ soil | site_crop_yr)
```


```{r, echo= FALSE}
cn_means = lsmeans(cn.mod, ~ soil | site_crop_yr , contr = "pairwise", adjust = "none")
```


```{r, echo= FALSE}
cn_meansCLD <- CLD(cn_means, alpha=0.05, Letters=letters, adjust="none", sort=FALSE, reverse=FALSE)
cn_meansCLD
```

### Corn Yield Figure
```{r, echo= FALSE}
CN_meansCLD$Soil= factor(CN_meansCLD$Soil, levels=c("CT", "NT", "CCET", "CCPT","CCFH","CCLT"))
ylab.text1= expression("Yield kg ha"^"-1")

CNYield_SoilbySiteYR= 
  ggplot(CN_meansCLD, aes(x= Soil, y= lsmean, label= .group, fill= Site_crop_yr))+
         geom_point(aes(),stat= "identity")+
        facet_grid(~Site_crop_yr)+
         theme_bw()+
         geom_text(nudge_y= 1400, size = 4)+
         theme(panel.grid.major=element_blank(), panel.grid.minor= element_blank(),
        plot.title= element_text(size=16),
        axis.title.x=element_text(size= 15),
        axis.title.y= element_text(size= 15),
        axis.text= element_text(size= 11))+
         ylim(0,19000)+
    geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .3)+
    labs(title= "Corn Yield", x= "Soil Management Practice", y= ylab.text1)+
  ggsave("CNYield_SoilbySiteYR.jpeg", height= 6, width= 10, dpi=600)

CNYield_SoilbySiteYR
```

```{r, include= FALSE}
CN.mod1= lmer(Yield~ Year*Location*Soil*PRE + (1|Site_crop_yr:Rep), data=Corn)

qqnorm(resid(CN.mod1))

plot(CN.mod1)

anova(CN.mod1)

#Composite
CN_means= lsmeans(CN.mod1 ,~ Soil*Year|Location, contr="pairwise", adjust="none", type="response")
CN_meansCLD<- CLD(CN_means, alpha=0.05, Letters=letters, adjust="none", sort=FALSE, reverse=FALSE)
CN_meansCLD

#Arlington alone
ARLCN.mod1= lmer(Yield~ Year*Location*Soil*PRE + (1|Site_crop_yr:Rep), data=Corn)

```


```{r, include= FALSE}
lsm1= lsmeans(CN.mod, ~ Soil|Site_crop_yr, contr="pairwise", adjust="none", type= "response")
Corn_Site_Soil= CLD(lsm1, alpha=0.05, Letters=letters, adjust="none", sort=FALSE, reversed=FALSE)
Corn_Site_Soil


```



# Soybean Yield

### Model and ANOVA
```{r}
SB.mod= lmer(Yield~ Site_crop_yr*Soil*PRE + (1|Site_crop_yr), data=Soybean)

```

```{r, echo= FALSE}
qqnorm(resid(SB.mod))

plot(SB.mod)
#Assumption appear to be met visually, There is some "trailing off" occurring at the bottom of the QQ Plot. 

#square root transform for kicks

SB.mod1= lmer(sqrt(Yield)~ Site_crop_yr*Soil*PRE + (1|Site_crop_yr), data=Soybean)

qqnorm(resid(SB.mod1))

plot(SB.mod1)
#Didn't improve
```
Assumptions for normality and equal variance of residuals appear to be visually met, proceed with ANOVA.

```{r}
anova(SB.mod)
#Nothing was significant at alpha= 0.05 but 3-way interaction almost significant. Maybe Clean the data?
```
Nothing was significant at alpha=0.05. The 3-way interaction is dangerously close which makes me uncomfortable.

```{r}
SB.mod1= lmer(Yield~ Year*Location*Soil*PRE + (1|Site_crop_yr:Rep), data=Soybean)

qqnorm(resid(SB.mod1))

plot(SB.mod1)

anova(SB.mod1)

SB_means= lsmeans(SB.mod1 ,~ Soil*Year|Location, contr="pairwise", adjust="none", type="response")
SB_meansCLD<- CLD(SB_means, alpha=0.05, Letters=letters, adjust="none", sort=FALSE, reverse=FALSE)
SB_meansCLD

```

What do I do about that P-value?!?!?!?!