---
title: "Systems Project Crop Productivity"
author: "Kolby Grint"
date: "11/10/2020"
output:
  pdf_document: default 
  html_document: default
---


```{r, include= FALSE}
library(car)
library(emmeans)
library(lme4)
library(lmerTest)
library(patchwork)
library(glmmTMB)
library(tidyverse)
```


```{r}
data = read_csv("SystemsProjectMasterDataforR.csv") %>% 
  mutate_if(is.character, as.factor) %>% 
  janitor::clean_names() %>% 
  mutate(
    year = as_factor(year),
    rep = as_factor(rep)
  )
data
```

```{r}
corn = filter(data, crop == "Corn")
soybean= filter(data, crop == "Soybean")
```


# Corn Yield

```{r}
corn %>% 
  ggplot(aes(x = yield)) +
  geom_density() # it looks normal

shapiro.test(corn$yield) # Shapiro-Wilk shows your data is normal but near to 0.5. Go ahead!

bartlett.test(yield ~ soil, data = corn) # homogeneity of variances OK also
```


### Model and ANOVA

```{r}
cn.mod = lmer(yield ~ site_crop_yr * soil * pre + (1 | site_crop_yr : rep), data = corn)
```


```{r, echo= FALSE}
qqnorm(resid(cn.mod))

plot(cn.mod)
```
I think assumptions for normality and equal variance are met.


```{r}
anova(cn.mod)
#Soil and site-crop-year fixed effects and Site-year:Soil was significant
```

Site-crop-year:soil management interaction, soil management fixed effect, and site-crop-year fixed effect are all significant. Proceeded to separate means by looking at soil management practices within each site-crop-year. Results displayed in the figure below.

```{r}
emmip(cn.mod, ~ soil | site_crop_yr)
```


```{r, echo= FALSE}
cn_means = emmeans(cn.mod, ~ soil | site_crop_yr , contr = "pairwise", adjust = "none")

cn_means$emmeans
```


```{r }
if(requireNamespace("multcomp")) {
  cn_meansCLD <- multcomp::cld(cn_means$emmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)
}

cn_meansCLD
```


### Corn Yield Figure

```{r, echo= FALSE}
cn_meansCLD <- as_tibble(cn_meansCLD) %>% 
  mutate(
    site_crop_yr = fct_recode(site_crop_yr, # do the same for soil management
      "Arlington 2019" = "ARL_CN_19",
      "Arlington 2020" = "ARL_CN_20",
      "Lancaster 2019" = "LAN_CN_19",
      "Lancaster 2020" = "LAN_CN_20" # recoding with full names are better than abbreviations
    )
  )
  

ggplot(cn_meansCLD, aes(x= fct_reorder(soil, emmean), y= emmean, 
                        label= .group)) +
  geom_point() +
  geom_errorbar(aes(ymin= lower.CL, ymax= upper.CL), width= .2) +
  facet_grid(~ fct_reorder(factor(site_crop_yr), emmean, .fun = length)) +
  geom_text(nudge_y= 2500, size = 4) +
  theme_bw() +
  theme(panel.grid.major=element_blank(), panel.grid.minor= element_blank(),
        plot.title= element_text(size=16),
        axis.title.x=element_text(size= 15),
        axis.title.y= element_text(size= 15),
        axis.text= element_text(size= 11)) +
  ylim(0, 19000) +
  coord_flip() +
  labs(title= "Corn Yield", x= "Soil Management practice", y= expression(paste("Yield (kg ha "^"-1",")"))) +
  ggsave("CNYield_SoilbySiteYR.jpeg", height= 6, width= 10, dpi=600)
```

```{r, include= FALSE}
cn.mod1 = lmer(yield ~ year * location * soil * pre + (1 | site_crop_yr:rep), data = corn)

qqnorm(resid(cn.mod1))

plot(cn.mod1)

anova(cn.mod1)

#Composite
cn_means1 = emmeans(cn.mod1 ,~ soil * year | location, contr = "pairwise", adjust="none", type="response")


if(requireNamespace("multcomp")) {
  cn_meansCLD1 <- multcomp::cld(cn_means$emmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)
}
cn_meansCLD1


#Arlington alone
#ARLCN.mod1= lmer(yield ~ year * location * soil * pre + (1 | site_crop_yr:rep), data = corn)

```


```{r, include= FALSE}
lsm1= lsmeans(CN.mod, ~ Soil|Site_crop_yr, contr="pairwise", adjust="none", type= "response")
Corn_Site_Soil= CLD(lsm1, alpha=0.05, Letters=letters, adjust="none", sort=FALSE, reversed=FALSE)
Corn_Site_Soil
```



# Soybean Yield


```{r}
soybean %>% 
  ggplot(aes(x = yield)) +
  geom_density() # it looks normal except to this weird drop in the center
```



### Model and ANOVA
```{r}
sb.mod = lmer(yield ~ site_crop_yr * soil * pre + (1 | site_crop_yr), data = soybean)
```

```{r, echo= FALSE}
qqnorm(resid(sb.mod))

plot(sb.mod)
#Assumption appear to be met visually, There is some "trailing off" occurring at the bottom of the QQ Plot. 

#square root transform for kicks

sb.mod1 = lmer(sqrt(yield) ~ site_crop_yr * soil * pre + (1 | site_crop_yr), data = soybean)

qqnorm(resid(sb.mod1))

plot(sb.mod1)
#Didn't improve
```
Assumptions for normality and equal variance of residuals appear to be visually met, proceed with ANOVA.

```{r}
anova(sb.mod)
#Nothing was significant at alpha= 0.05 but 3-way interaction almost significant. Maybe Clean the data?
```
Nothing was significant at alpha=0.05. The 3-way interaction is dangerously close which makes me uncomfortable.


```{r}
sb.mod1 = lmer(yield ~ year * location * soil * pre + (1 | site_crop_yr:rep), 
               data = soybean)

qqnorm(resid(sb.mod1))

plot(sb.mod1)

anova(sb.mod1) # I would look at location:soil:pre 

sb_means1 = emmeans(sb.mod1, ~ soil * pre | location, contr = "pairwise", adjust="none", type="response")


if(requireNamespace("multcomp")) {
  sb_meansCLD1 <- multcomp::cld(sb_means1$emmeans, alpha=0.05, Letters=letters, adjust="none", sort=TRUE, reverse=TRUE)
}

sb_meansCLD1
```

What do I do about that P-value?!?!?!?!
